Milestone 2: Datasets Generation

### 2019-10-18 perf_release_criteria/ms_2_dataset_generation.Rmd
Cleaning up.

---
title: 'Milestone 2: Datasets Generation'
output:
  html_document:
    df_print: paged
---

@@

upload_try <- gcs_upload(image_file_path, name = image_file_path)
upload_try
```
```{r}
upload_try
```

>>>>

---
title: 'Milestone 2: Datasets Generation'
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

@@

upload_try <- gcs_upload(image_file_path, name = image_file_path)
upload_try
```
